% Section P: Participation

\renewcommand{\thesection}{P}
\section{Participation}

\subsection{Team Eligibility}

\subsubsection{Participant Requirements}
\begin{itemize}[noitemsep]
    \item Each participant may be a member of one team only
    \item Only undergraduate or master's degree students are eligible
    \item Doctoral candidates and postgraduates may not join competing teams
    \item Participants may compete for maximum five competition cycles from first registration
    \item Team members must be at least 18 years old
\end{itemize}

\subsubsection{Team Composition}
\begin{itemize}[noitemsep]
    \item Each team must designate one Team Captain as primary contact
    \item Teams may have maximum 50 members
    \item Members organize internally by skills and project needs
    \item At least one Faculty Advisor required per team
\end{itemize}

\subsubsection{Institutional Limitations}
\begin{itemize}[noitemsep]
    \item Each university may register one official team only
    \item Multi-university teams permitted under single host institution
    \item Teams must develop projects independently
    \item Faculty advisors limited to mentorship role only
\end{itemize}

\subsection{Team Roles}

\subsubsection{Team Captain}
The Team Captain serves as official representative and primary contact with the organizing committee. Responsibilities include:
\begin{itemize}[noitemsep]
    \item Coordinating all official communications
    \item Ensuring timely documentation submission
    \item Representing team in briefings and reviews
    \item Overseeing internal coordination
\end{itemize}

Captain changes require written justification and committee approval.

\subsubsection{Faculty Advisor}
Each team requires at least one Faculty Advisor affiliated with the host institution. The advisor provides academic guidance and institutional support but must not directly develop technical deliverables. All core design and documentation must remain student responsibility.

\subsubsection{Technical Advisory}
While not mandatory, teams are strongly encouraged to have at least one faculty advisor with relevant background in physics, electrical engineering, or related fields.

\subsection{Intellectual Property}

\subsubsection{}
All technical designs, simulations, and documentation submitted to ELIAC will be released under MIT License. Teams retain full attribution rights.

\subsubsection{}
Teams may publish work independently only after official publication in ELIAC proceedings. The organizing committee reserves rights for educational and promotional use with attribution.

\subsection{Code of Conduct}

\subsubsection{}
All participants must maintain professional standards:
\begin{itemize}[noitemsep]
    \item Academic integrity: All work must be original to the team
    \item Professional behavior: Respectful interaction required
    \item Fair competition: Sabotage or unfair practices prohibited
\end{itemize}

\subsubsection{}
The organizing committee reserves the right to:
\begin{itemize}[noitemsep]
    \item Issue warnings for minor infractions
    \item Deduct 10-50 points for conduct violations
    \item Disqualify teams for serious breaches with written justification
\end{itemize}

Appeals must be submitted within 48 hours of notification.

\subsection{Competition Integrity}

\subsubsection{}
The organizing committee commits to maintaining fair and unbiased evaluation through:
\begin{itemize}[noitemsep]
    \item Conflict of interest declarations
    \item Standardized evaluation rubrics
    \item Neutral institutional stance
    \item Transparent scoring with feedback
\end{itemize}

\subsection{Collaboration Policy}

\subsubsection{}
Teams may freely share general knowledge and published resources. Inter-team physics discussions are encouraged.

\subsubsection{}
Prohibited: Direct sharing of simulation files, custom code, or CAD models between teams. Extensive external assistance that replaces student effort. Teams must disclose significant external contributions.

\subsection{Withdrawal and Substitution}

\subsubsection{}
Team withdrawal permitted up to 30 days before final submission. No registration refunds after this date.

\subsubsection{}
Member substitution allowed with restrictions:
\begin{itemize}[noitemsep]
    \item Before preliminary submission: Unlimited with notification
    \item After preliminary submission: Maximum 2 with justification
    \item After final submission: Medical emergency only
\end{itemize}

All changes require faculty advisor approval and official documentation.